\LARGE \bf Preparation of Papers for IEEE Sponsored Conferences \& Symposia*

### 2017-06-11 implementation.tex
.

The presented technique was prototyped as a tool: PWA-Rel.  We
compared it against S3CAM~\cite{zutshi2014multiple} on several
academic benchmarks. Below, we present the details of the
implementation and the benchmarks used.

\subsection{Implementation}
PWA-Rel was implemented in Python. Its different parts comprised of
the (a) abstraction graph generation, (b) regression analysis and (c)
BMC. S3CAM was used to compute (a). To compute (b), OLS regression
routines were used from Scikit-learn~\cite{pedregosa2011scikit}, a
Python module for machine learning. Finally, the The bounded model
checking (c) was done using the SAL model checker~\cite{SAL-SRI},
which used Yices2~\cite{dutertre2014yices} as the SMT solver. A naive
alternative linear programming (LP) based model checker, specific to
the PWA relational abstractions was implemented utilizing PyGLPK.
Specifically, each path of the graph $G^R$ was sent to the lp solver
PyGLPK and checked for feasibility. If feasible, the checker returned
a concrete counter-example.

PWA-Rel uses S3CAM to discover the abstraction graph $G$, which is
then filtered to remove the nodes from which error nodes are not
reachable. In all our experiments we used $1$-relational modeling to
create the transition system from $G$. This was determined to be a
good trade-off between longer simulations and increase in precision,
with respect to the mentioned benchmarks.

Using the BMC, we checked for the given safety property. If a concrete
trace was obtained, it was further checked for reproducibility by
sampling and simulating its `neighborhood' with the $\simulate$
function. We define `neighborhood' as the abstract states
corresponding to the returned concrete trace.  Specifically, $100$
samples were uniformly randomly chosen and simulated and tested for
error traces. This procedure can also be extended to obtaining
different discrete sequences or discrete trace sequences from the
model checker by requesting distinct counter-examples.

@@

\subsection{Evaluation}
We tabulate our preliminary evaluation in \tabref{res-rel}. We used
the more difficult benchmarks described in \cite{zutshi2014multiple},
including the Van der Pol oscillator, Brusselator, Lorenz attractor
and the Navigation benchmark. PWA-Rel and S3CAM were tested $10$ times
with different seeds and their running times were averaged. We tabulate
both the total time taken by PWA-Rel+SAL and PWA-Rel+LP to compute the
counter-example and compare against an implementation of S3CAM.
Different abstraction parameters are used for S3CAM and PWA-Rel, due
to the differences in which they operate. PWA-Rel requires a finer
abstraction to begin with in order to minimize the modeling errors.
On the other hand, a coarser abstraction as the initial abstraction is
works better for S3CAM due to the expensive refinement procedure
involved.

>>>>

The presented technique was prototyped as a tool: PWA-Rel.  We
compared it against S3CAM~\cite{zutshi2014multiple} on several
benchmarks. Below, we present the details of the implementation and
the benchmarks used.

\subsection{Implementation}

PWA-Rel is implemented in Python. It uses S3CAM to generate the graph
abstraction and regression routines from
Scikit-learn~\cite{pedregosa2011scikit} to compute
$\RTSAbstraction{\epsilon}{\System}$ of the given system $\System$.
It then constructs relational abstraction and uses a bounded model
checker to find a counter-example to the given property in
$\RTSAbstraction{\epsilon}{\System}$. Finally, using simulations, it
confirms if the counter-example is valid for $\System$, in which case
a successfull falsification run is concluded.

To check the transition system, PWA-Rel can either invoke symbolic
bounded model checkers or explicit model checkers. For symbolic BMC,
the off-the-shelf SAL modelchecker~\cite{SAL-SRI} is used. It is
configured to encode the problem as a single query for a given depth
$k$, where $k$ is the bound on the length of the counter-example. It
was computed by the length of the abstract counter-examples found. SAL
uses the SMT solver Yices2~\cite{dutertre2014yices} to solve the
encoded SMT constraints.

% Two symbolic BMC were tried to compare scalability; the off-the-shelf
% SAL model checker~\cite{SAL-SRI} and SatExBMC. Both model checkers
% were configured to encode the problem as a single query for the given
% depth. SAL uses the SMT solver Yices2~\cite{dutertre2014yices}, while
% SatExBMC uses SatEx~\cite{shoukry2017smc}. SatEx differs from Yices2
% (and other sound SMT solvers) in two aspects, (a) it is a lazy SMT
% solver and (b) uses approximate convex optimization routines (via
% CPLEX). Although (b) makes it unsound, it is not a concern for our
% falsification procedure as it is based off approximate models.

Explicit model checking was implemented out using a naive DFS
(depth-first-exploration) stratergy, wherein, each abstract path is
enumerated and checked for feasibility using a an optimization
routine. Intefaces to various solvers were implemented, including GLPK
and Ipopt. If feasible, the returned concrete counter-example is
simulated and checked for existance in $\System$. Also, PWA-Rel
extracts the bounds on the initial parameters by formulating multiple
optimization problems. The bounds can be regarded as an over-appr

% If the existance check fails, multiple
% parameter values can be sampled within the determined bounds to search
% for counter-examples in the neighbhourhood of the returned concrete
% counter-example.

% PWA-Rel uses S3CAM to discover the abstraction graph $G$, which is
% then filtered to remove the nodes from which error nodes are not
% reachable. In all our experiments we used $1$-relational modeling to
% create the transition system from $G$. This was determined to be a
% good trade-off between longer simulations and increase in precision,
% with respect to the mentioned benchmarks.
% \todo{$1$-relational modeling was used}

Using BMC, we checked for the given safety property. If a concrete
trace was obtained, it was further checked for reproducibility by
sampling and simulating its `neighborhood' with the $\simulate$
function. We define `neighborhood' as the abstract states
corresponding to the returned concrete trace.  Specifically, $100$
samples were uniformly randomly chosen and simulated and tested for
error traces. This procedure can also be extended to obtaining
different discrete sequences or discrete trace sequences from the
model checker by requesting distinct counter-examples.

@@

\subsection{Evaluation}

We benchmarked our implementation and compared it with S3CAM.  The
preliminary results are tabulated in~\tabref{res-rel}. We used few of
the benchmarks described in \cite{zutshi2014multiple}, including the
Van der Pol oscillator, Brusselator, Lorenz attractor and the
Navigation benchmark. We also tried PWA-Rel on the insulin
benchmark~\cite{chenformal} and lane change maneuver
benchmark~\cite{althoff2012reachability}. PWA-Rel was compared with
S3CAM by running both $10$ times with different seeds (as both use
randomized algorithms), and their running times were averaged. PWA-Rel
was evluated with both the symbolic BMC SAL (PWA-Rel+SAL) and the
explicit BMC (PWA-Rel+OPT).  \todo{SatEx was also tried, but ...}. We
tabulate both the total time taken by PWA-Rel+SAL and PWA-Rel+OPT to
compute the counter-example and compare against an implementation of
S3CAM.  Different abstraction parameters are used for S3CAM and
PWA-Rel, due to the differences in which they operate. PWA-Rel
requires a finer abstraction to begin with in order to minimize the
modeling errors. On the other hand, a coarser abstraction as the
initial abstraction works better for S3CAM due to the expensive
refinement procedure involved.~\footnote{In all our experiments we
used $1$-relational modeling to create the transition system from $G$.
This was determined to be a good trade-off between longer simulations
and increase in precision, with respect to the mentioned benchmarks.}
